\section{AHTR One-Third Assembly Optimization Results Discussion}
\label{sec:assem-discussion}
Chapter \ref{chap:ahtr-plank-opt-results} characterized the \gls{AHTR} plank model's 
driving factors for each reactor optimization objective and their relationship with 
one another. 
This section utilizes the previous \gls{AHTR} plank characterizations and conduct 
a deep-dive to verify if the same reactor optimization objective driving factors apply 
to the \gls{AHTR} one-third assembly model. 
I also analyze how their combined effects result in the optimal reactor models found by 
the multi-objective optimization simulations. 

\subsection{Discussion: Minimize $PF_{total}$ Objective}
\label{sec:assem-discussion-pf}
\paragraph{Simulation a-1a}
In Section \ref{sec:assem-1-obj-pf}'s simulation a-1a, I conducted a single-objective 
optimization simulation to minimize the one-third assembly's total fuel packing fraction 
($PF_{total}$) by varying $PF_{total}$ and TRISO distribution. 
In simulation a-1a, \gls{ROLLO} found that an \gls{AHTR} one-third assembly model with 
the most-minimized $PF_{total}$ has $PF_{total}= xx$ and a TRISO distribution xx 

Section \ref{sec:plank-discussion-pf} concluded that for the \gls{AHTR} plank model, 
the minimize $PF_{total}$ objective is driven by maximizing the total fission reaction 
rates. 
I ran a simulation for constant $PF_{total}$ = xx TRISO distribution and compared its 
fission reaction rate with the center-peaking TRISO distribution. 

\paragraph{Simulation p-1d}
In Section \ref{sec:assem-1-obj-pf}'s simulation a-1d, I conducted a single-objective 
optimization simulation to minimize total fuel packing fraction ($PF_{total}$) by 
varying $PF_{total}$ and coolant channel shape. 
In simulation a-1a, \gls{ROLLO} found that there is no correlation 
between $PF_{total}$ and coolant channel shape (demonstrated in Figure 
\ref{fig:a-1d}). 

\paragraph{Summary}
I verified that the minimize $PF_{total}$ objective for the \gls{AHTR} one-third assembly 
model is also driven by maximizing the total fission reaction rates. 
The minimize $PF_{total}$ objective has correlations with the following input parameters: 
$PF_{total}$ and TRISO packing fraction distribution. 
The objective has no correlation with coolant channel shape input parameter. 

\subsection{Discussion: Minimize $T_{max}$ Objective}
\label{sec:assem-discussion-temp}

\subsection{Discussion: Minimize $PPF_{fuel}$ Objective}
\label{sec:assem-discussion-ppf}
\paragraph{Simulation a-1c}
In Section \ref{sec:assem-1-obj-ppf}'s simulation a-1c, I conducted a single-objective 
optimization simulation to minimize fuel-normalized power peaking factor ($PPF_{fuel}$) 
by varying TRISO distribution. 
In simulation a-1c, \gls{ROLLO} found that for $PF_{total}$ = 0.06, an \gls{AHTR} 
one-third assembly model with TRISO distribution xx. 

Section \ref{sec:assem-discussion-pf} concluded that for the \gls{AHTR} one-third 
assembly model, the minimize $PPF_{fuel}$ objective is driven by flattening thermal 
(Group 4) flux distribution. 
I compare the flux distributions for the most-minimized $PPF_{fuel}$ reactor model and 
the maximum $PPF_{fuel}$ reactor model in the final generation of simulation a-1c. 

\paragraph{Simulation a-2b}


\subsection{Discussion: Multi-Objective Optimization}
\label{sec:assem-discussion-multi}

\section{Summary}

% talk about p-3b result, what is recommended for the AHTR assembly's geometry. 