\chapter{Conclusions and Future Work}
\glsresetall
\label{chap:concl}

Additive manufacturing of reactor core components removes the geometric constraints
imposed by conventional manufacturing, such as fuel planks slabs and fuel rod 
cylinders, enabling further optimization and improvement of core geometries. 
Wide-spread adoption of additive manufacturing methods in the nuclear industry
could drastically reduce fabrication costs and deployment timelines, and improve 
reactor safety. 
Fully benefitting from the new ability to 3D print reactor components requires further 
research into reactor generative design optimization. 
This dissertation explores the new design space enabled by additive manufacturing 
by designing and applying the flexible and open-source \gls{ROLLO} tool to optimize 
the \gls{AHTR} for non-conventional geometries and parameters. 
I successfully explored the \gls{AHTR}'s arbitrary geometry design space by completing 
these three dissertation objectives: 
\begin{enumerate}
    \item I furthered our understanding of the \gls{AHTR} design's complexities 
    through neutronics and thermal-hydraulics modeling by participating in the 
    \gls{OECD} \gls{NEA} \gls{FHR} benchmark.
    \item I developed the open-source \gls{ROLLO} tool that enables generative reactor 
    design using evolutionary algorithm optimization for non-conventional reactor 
    geometries and fuel distributions.
    \item I applied \gls{ROLLO} to conduct generative \gls{AHTR} design optimization.
    \gls{ROLLO} generated \gls{AHTR} designs with varying fuel amounts, fuel 
    distributions, and coolant channel shapes that optimize for three key reactor 
    performance metrics: minimize total fuel amount, maximize heat transfer, and 
    minimize power peaking.
\end{enumerate}
Chapter \ref{chap:fhr-benchmark} addressed objective 1, chapter \ref{chap:rollo} 
addressed objective 2, and chapters \ref{chap:method}, \ref{chap:ahtr-plank-opt-results}, 
and \ref{chap:ahtr-assem-opt-results} addressed objective 3. 

Chapter \ref{chap:fhr-benchmark} reported the \gls{FHR} benchmark Phase I-A and I-B 
results, demonstrating the \gls{AHTR}'s passive safety behavior with 
negative temperature coefficients. 
A comparison of $k_{eff}$ results between the reference case and the \gls{AHTR} 
configuration with high heavy metal loading demonstrated that increased fuel 
packing does not always correspond with increased $k_{eff}$ due to self-shielding 
effects.
Chapter \ref{chap:fhr-benchmark} also reported the \gls{AHTR} full assembly temperature 
model results. 
The temperature distribution peaked in the fuel stripes near the spacers, 
highlighting to reactor designers that spacer material and location in the 
\gls{AHTR} geometry impact temperature peaks.  
Through participation in the \gls{FHR} benchmark, this dissertation contributes to 
deepening our understanding of the promising \gls{AHTR} technology. 

Chapter \ref{chap:rollo} described the \gls{ROLLO} tool developed for this 
dissertation. 
\gls{ROLLO} is a Python package that applies evolutionary algorithm 
optimization techniques to generate nuclear reactor designs that meet user-defined 
objectives and constraints based on user-defined input value ranges. 
\gls{ROLLO} enables reactor designers to optimize any reactor model using robust 
evolutionary algorithm methods without going through the cumbersome process of setting up 
an evolutionary algorithm framework, selecting appropriate hyperparameters, and 
setting up parallelization.
\gls{ROLLO} is effective, flexible, accessible, parallel, reproducible, usable, and 
hosted on Github \cite{chee_rollo_2021}. 

Chapter \ref{chap:method} described the modeling and optimization methodology of the 
\gls{AHTR} plank and one-third assembly optimization conducted using the \gls{ROLLO} 
software.
I varied the following \gls{AHTR} plank and one-third assembly input parameters: 
\gls{TRISO} packing fraction distribution ($\rho_{TRISO}(\vec{r})$), total fuel 
packing fraction ($PF_{total}$), and coolant channel shape; to minimize 
the following objectives: total fuel packing fraction ($PF_{total}$), maximum 
temperature ($T_{max}$), and fuel-normalized power peaking factor ($PPF_{fuel}$). 

Chapter \ref{chap:ahtr-plank-opt-results} reported the \gls{AHTR} plank's 
\gls{ROLLO} optimization results.
I characterized each objective's driving factors and relationship 
with each input parameter from the results. 
I determined that the minimize $PF_{total}$ objective is driven by maximizing the plank's 
total fission reaction rate and influences oscillations in the TRISO distribution to 
achieve the objective. 
I determined that the minimize $PPF_{fuel}$ objective is driven by flattening the plank's
thermal flux distribution and influences $PF_{total}$ and oscillations in the TRISO 
distribution to achieve the objective.
I determined that the minimize $T_{max}$ objective flattens TRISO distribution and 
maximizes coolant channel shape's radius values to achieve the objective.
The multi-objective optimization simulation results showed that 
the minimize $PF_{total}$ and $PPF_{fuel}$ driving factors influence each other 
resulting in unexpected TRISO distributions at different $PF_{total}$ values. 
Further optimization of the \gls{AHTR} design will benefit from awareness 
of the relationship between the objectives. 
The objectives' characterizations for the simple \gls{AHTR} plank model provide insights 
to better understand Chapter \ref{chap:ahtr-assem-opt-results}'s multi-objective 
optimization of the complex \gls{AHTR} one-third assembly model.   

Chapter \ref{chap:ahtr-assem-opt-results} reported the \gls{AHTR} one-third assembly's
\gls{ROLLO} optimization results.
I verified that the one-third assembly objectives follow the same driving 
factors as the \gls{AHTR} plank optimization objectives. 
Similar to the \gls{AHTR} plank optimization results, these results demonstrated that 
the minimize $PF_{total}$ and $PPF_{fuel}$ driving factors influence each other 
resulting in unexpected TRISO distributions at different $PF_{total}$ values. 
The results also demonstrated that the coolant channel shape variation did 
not have as high of an impact on $T_{max}$ as the \gls{TRISO} distribution variation.
The final and largest optimization problem is the one-third assembly multi-objective 
optimization that minimized all three objectives ($PF_{total}$, $T_{max}$, and 
$PPF_{fuel}$) while varying all the input parameters ($PF_{total}$, TRISO distribution, 
and coolant channel shape), also known as simulation a-3b-256. 
\gls{ROLLO} optimization simulation a-3b-256 ran for $\sim 3300$ Theta supercomputer 
node-hours with 8 generations and 256 reactor models per generation. 
Figure \ref{fig:assem-obj-3-all-256} showed the 38 reactor models on simulation 
a-3b-256's Pareto front that met all three objectives. 
The reactor models on the Pareto Front have different $PF_{total}$, TRISO distributions, 
and coolant channel shapes, depending on the extent each objective is minimized due 
to the nature of multi-objective optimization that results in a tradeoff between 
objectives. 
These results demonstrate that \gls{ROLLO}'s generative design optimization process 
provides the reactor designer with a set of equally good reactor models that minimize 
all objectives.

Chapters \ref{chap:ahtr-plank-opt-results} and \ref{chap:ahtr-assem-opt-results} 
demonstrated \gls{ROLLO}'s success in conducting multi-objective generative reactor 
design optimization. 
\gls{ROLLO} conducted a global search of the large reactor design space and successfully 
generated optimal reactor models on the Pareto front that satisfy all the objectives. 
\gls{ROLLO}'s generative design optimization process also gives reactor designers 
unique insight into the reactor design's problem domain and a sense of how 
sensitive each input parameter is in relation to the objectives. 
Once the \gls{ROLLO} search is complete, reactor designers gain a better intuition for 
the model's reactor physics and can view the narrower reactor design space that meets 
their defined objectives.   
From this point, it is up to the reactor designer to determine the importance of each 
objective for their purposes, then conduct further sensitivity analysis and 
use higher fidelity models to study the optimal design space before selecting 
the final reactor model.
By designing the \gls{ROLLO} tool and demonstrating \gls{ROLLO}'s success in 
optimization of the \gls{AHTR} beyond classical input parameters, this dissertation 
contributes to optimization tool development for reactors of the future. 

\section{Limitations and Future Work}
This dissertation demonstrated results for the \gls{FHR} benchmark's Phases I-A and I-B.
The \gls{FHR} benchmark is an ongoing project; thus, future work includes further 
contributions to the benchmark's Phases I-C, II, and III. 

This dissertation demonstrated \gls{ROLLO}'s success in conducting multi-objective 
generative reactor design optimization. 
\gls{ROLLO} could be further improved in the following ways: parallelization speed-up, 
JSON input file validation improvement, error message clarity, contingency kill 
switch implementation to minimize wasted compute time, unit testing expansion, 
and more nuclear reactor modeling software \gls{ROLLO} coupling examples.  
These issues are detailed at \url{https://github.com/arfc/rollo/issues}.

This dissertation's generative design optimization of the \gls{AHTR} model used sine 
distribution variations to govern the \gls{TRISO} packing fraction distribution and  
cylinder radius variation to generate sinusoidal-like patterned coolant channel shapes. 
These input parameter variations are only one way to represent the \gls{AHTR} 
geometry. 
There are other ways to represent the geometry that might give \gls{ROLLO} more 
freedom to explore a larger design space and generate more optimized designs. 
Future reactor designers could consider topology optimization to optimize coolant 
channel shape further.
The major limitation is the computational cost of modeling fluid flow in complex 
coolant channel designs. 

Nuclear reactors represent physics interactions and feedbacks between thermal-hydraulics, 
neutronics, material performance, structural mechanics, chemistry, and more. 
Multiphysics modeling is the practice of accounting for these physics interactions 
during design and analysis. 
This dissertation's generative design optimization modeled the \gls{AHTR} model's 
beginning of life neutronics and temperature. 
Many multiphysics components were not included in this study; their inclusion in
the \gls{AHTR} optimization process might impact the optimal \gls{AHTR} designs 
found by \gls{ROLLO}. 
Future work includes taking into account the effect of burnup, structural mechanics, 
thermal stresses, chemistry, and higher fidelity thermal-hydraulics for \gls{AHTR} 
model optimization. 
This relies on further developments in the reactor multiphysics modeling 
field through advanced coupling methods and narrowing down the important coupled 
physics interactions in the reactor types. 
The optimization work conducted in this dissertation utilized $\sim 50000$ node-hours 
on the BlueWaters and Theta supercomputers. 
Optimization work that models more complex reactor geometries with more 
multiphysics components will require even more compute time. 
Therefore, the feasibility of further optimization work also relies on speed-ups 
in software compute time and increased availability of compute time to 
conduct these simulations. 

As additive manufacturing technology advances and the \gls{TCR} program 
demonstrates the first 3D printed operational reactor, more reactor designers 
will begin to explore the vast design space enabled by 3D printing. 
\gls{ROLLO} can be easily used to optimize any reactor type. 
Future work includes utilizing \gls{ROLLO} to vary more reactor types for arbitrary
geometries and parameters and optimize for objectives that address the many-faceted 
multiphysics interactions and feedbacks in the reactors.